**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2020-12-10 paper/paper.Rmd
Paste some text from ASM abstract

@@

- 16S rRNA gene sequence datasets from human gut, mouse gut, marine, and soil environments as well as the greengenes, silva, and RDP public databases were processed with mothur and clustered _de novo_ with mothur's OptiClust algorithm.
- All clustering was performed at a distance threshold of 0.03 and repeated with 100 different random seeds.
- The Matthews Correlation Coefficient was calculated to serve as a measure of OTU quality.

@@

@@

>>>>

Assigning amplicon sequences to Operational Taxonomic Units (OTUs) is an
important step in characterizing the composition of microbial communities across
large datasets. OptiClust, a _de novo_ OTU clustering method in the mothur
program, has been shown to produce higher quality OTU assignments than other
methods and at comparable or faster speeds [@westcott_opticlust_2017;
@schloss_introducing_2009]. A notable difference between _de novo_ clustering
and database-dependent methods is that OTU assignments clustered with _de novo_
methods are not stable when new sequences are added to a dataset
[@westcott_novo_2015]. However, in some cases one may wish to incorporate new
samples into a previously clustered dataset without performing clustering again
on all sequences, such as when deploying a machine learning model where OTUs are
features [@topcuoglu_effective_2019]. To provide an efficient and robust method
to fit amplicon sequence data to existing OTUs, we developed the OptiFit
algorithm as a new component of the mothur program.

- TODO: Describe OptiClust and vsearch.

@@

- TODO: brief description of OptiFit algorithm. the method we came up with is the result. OptiClust paper had toy example to walk through the algorithm. 
- TODO: Paragraph at beginning to describe datasets: why picked, how processed.

We used four published datasets isolated from soil
[@johnston_metagenomics_2016], marine [@henson_artificial_2016], mouse
[@schloss_stabilization_2012], and human [@baxter_microbiota-based_2016]
samples.

- 16S rRNA gene sequence datasets from human gut, mouse gut, marine, and soil environments as well as the greengenes, silva, and RDP public databases were processed with mothur and clustered _de novo_ with mothur's OptiClust algorithm.
- All clustering was performed at a distance threshold of 0.03 and repeated with 100 different random seeds.
- The Matthews Correlation Coefficient was calculated to serve as a measure of OTU quality. OTU quality was evaluated using the Matthews Correlation
Coefficient (MCC) with a sequence dissimilarity threshold of 0.03% as described
previously [@schloss_application_2016; @westcott_novo_2015].

@@

- TODO: compare optifit performance for split dataset vs public database
- TODO: double-check with Sarah that MCCs are from full OTU dataset or just query sequnce OTUs
- TODO: double-check reference fractions aren't flipped (fraction mapped plot looks weird)

@@

- TODO: move this into first section with public database.
- vsearch is more permissive than mothur (radius vs diameter with 0.03 dissimilarity threshold).
